### 2019-08-15 report/chapter03.Rnw
Update thesis

missing.year.count <- sum(is.na(data$study.year)) + length(c(which(data$study.year < 1920), which(data$study.year > 2019)))

@@

\section{Cochrane Systematic Reviews}
Cochrane has specialized on systematic reviews in clinical science. Certain knowledge of standards and principles of the organization may help to assess the quality and the properties of the dataset. The following information stems from the Cochrane Handbook for Systematic Reviews \citep{cochrane.handbook}. \\
The definition of a systematic review is that it ``attempts to collate all empirical evidence that fits pre-specified eligibility criteria in order to answer a specific research question.'' Thus, the ``key properties of a review are'':

@@

\item MEDLINE. MEDLINE includes over 16 million references to journal articles. 5,200 journals publishing in 27 languages are indexed for MEDLINE. PubMed gives access to a free version of MEDLINE with up-to-date citations. NLM gateway such as the Health Services Research Project, Meeting Abstracts and TOXLINE Subset for toxicology citations allows for search in both databases together with additional data from the US National Library of Medicine.
\item EMBASE. 4,800 Journals publishing in 30 languages are indexed to EMBASE, which includes more than 11 million records from 1974 onward. EMBASE.com also includes 7 million unique records from MEDLINE (1966 up to date) together with its own records. Additionally, EMBASE Classic allows access to digitized records from 1947 to 1973. EMBASE and MEDLINE each have around 1,800 journals not indexed in the other database.

@@

\item Citation Indexes. The database lists articles published in around 6,000 Journals with articles in which they have been cited and is available online as SciSearch. This form of search is known as cited reference searching.

@@

\item Grey Literature Databases. Approximately 10\% of the results in the Cochrane Library stems from conference abstracts and other grey literature. The Institute for Scientific and Technical Information in France provides access to entries of the previously closed System for Information on Grey Literature database of the European Association for Grey Literature Exploitation). Another source is the Healthcare Management Information Consortium (HMIC) database containing records from the Library and Information Services department of the Department of Health (DH) in England and the King's Fund Information and Library Service. The National Technical Information Service (NTIS) gives access to the results of US and non-US government-sponsored research, as well as technical report for most published results. References from newsletters, magazines and technical and annual reports in behavioral science, psychology and health are provided in the PsycEXTRA database which is linked to PsycINFO database.

@@

\section{Structure and Variables}
The dataset consists of \Sexpr{length(unique(data$id))} systematic reviews from the Cochrane Library with \Sexpr{length(unique(data$study.name))} studies and \Sexpr{dim(data)[1]} results. A result is a outcome of a study, thus studies can contribute multiple results. The studies too a very large extent randomized and investigate the effects of healthcare and medical interventions and treatments. The reference to the treatment may be a placebo control or a different intervention or treatment. A result can not only be about efficacy of the treatments, but also about safety (adverse effects).\\
It will be continued with an example form the dataset. In Table \ref{barbiturate.row}, two results from a systematic review about barbiturates are shown as they are given in the dataset. As can be seen, further specifications are provided by the variables in the columns. \\
The \texttt{comparison.name} variable specifies \textit{what kind} of treatments or interventions are compared, the \texttt{outcome.name} variable \textit{how} it is compared, and the \texttt{subgroup.name} variable (not indicated in table) \textit{if and to what experimental subgroup} the result belongs. \\
The result is of a binary type, and the counts of events in the treatment group are in \texttt{events1} and of the control group in \texttt{events2} and the total number of participants are given in columns \texttt{total1} and \texttt{total2}. As can be seen, events denote here "death at the end of follow-up".

<<echo=FALSE, results = 'asis', warning =FALSE, message = FALSE>>=
print(xtable(barbi1, label = "barbiturate.row", digits = 0,
             caption = "Example of two results as given in the dataset. Events denotes the count of events in the treatment group while Events c the count of events in the group compared to. Further descriptive variables have been ommitted"), 
      include.rownames = F, size = "scriptsize")
@

Results are part of studies that are again part of a (systematic) review. This structure of a review is shown in Figure \ref{review.structure}.

\begin{figure}
\tikzstyle{every node}=[draw=black,thick,anchor=west]
\tikzstyle{selected}=[draw=red,fill=red!30]
\tikzstyle{optional}=[dashed,fill=gray!50]
\begin{tikzpicture}
[grow = right, anchor = west, 
  growth parent anchor=east, % added code
  parent anchor=east]
  \node {Review} [edge from parent fork right]
    child { node {Comparison 2}
      child { node {Outcome 2}}
      child { node {Outcome 1}
        child { node {Subgroup 2}}
        child { node {Subgroup 1}
          child  { node {Result 2}}
          child  { node {Result 1}}
          }}
    }
    child [missing] {}		
    child { node {Comparison 1  }};
\end{tikzpicture}
\caption{Structure of a hypothetical review with two different comparisons}
\label{review.structure}
\end{figure}

@@

\begin{table}[ht]
  \begin{center}
    \begin{tabular}{l l}
      \textbf{Variable} & \textbf{Description}\\
      \hline
      \texttt{id} & An id of the review for identification purposes.\\
      \hline
      \texttt{study.name} & Name of the study to which the result belongs.\\
      \texttt{study.year} & Year in which the study was published.\\
      \hline
      \texttt{comparison.name/.nr} & Specification of the interventions compared in the study and a \\ &unique number for the comparison.\\
      \texttt{comparison.id} & Specification of the comparison by a string of the type ``CMP-xxx'' \\ &for the xxx. comparison within the review.\\
      \texttt{outcome.name/.nr} & Specification by which outcome the interventions are compared\\ &and a unique number for the outcome.\\
      \texttt{outcome.id} & Specification of the outcome by a string of the type \\ &``CMP-xxx.xx'' for the xx. outcome of the xxx. comparison \\ &within the review.\\
      \texttt{subgroup.name/.nr} & Potentially indication of affiliation to subgroups and a unique \\ &number for the subgroup.\\
      \texttt{subgroup.id} & Specification of the comparison by a string of the type \\ &``CMP-xxx.yy.xx'' for the xx. subgroup for the yy. outcome \\ & of the xxx. comparison within the review.\\
      \texttt{outcome.measure} & Indication of the quantification method of the effect \\ &(of one intervention compared to the other).\\
      \texttt{outcome.measure.merged} & Indication of the quantification method of the effect, \\ &merged such that each method is uniquely classified.\\
      \texttt{outcome.flag} & A outcome flag to simplify programming; \\ &\texttt{DICH} for binary outcomes with fully available information \\ &on event counts,
      as given in a two-by-two \\ &table. \\ &\texttt{CONT} for continuous outcomes with available means and \\ &standard deviations. \\ & \texttt{IV} for all results with effects and standard errors but without \\ & the data necessary for their computation. \\ &\texttt{IPD} for individual patient data.\\
      \texttt{effect} & Measure of the effect given in the quantity denoted by \\ &\texttt{outcome measure}.\\
      \texttt{se} & Standard error of the measure of the effect.\\
      \texttt{events1/events2} & The counts of patients with an outcome if measurement/outcome \\ &is binary or dichotomous (1 for treatment group and 2 for control group).\\
      \texttt{total1/total2} & Number of patients in groups.\\
      \texttt{mean1/mean2} & Mean of patient measurements if outcome is continuous.\\
      \texttt{sd1/sd2} & Standard deviation of mean if outcome is continuous.
    \end{tabular}
  \caption{Dataset variable names and descriptions  \label{variable}}
  \label{variable}
  \end{center}
\end{table}

@@

The studies that are included in the reviews and have been published are most often from the years after 1980 (5\% quantile = \Sexpr{publication.year.range[1]}, 95\% quantile = \Sexpr{publication.year.range[6]},). The median of the publication years is \Sexpr{publication.year.range[3]}, the mean \Sexpr{publication.year.range[5]} and the quartiles are \Sexpr{publication.year.range[2]} and \Sexpr{publication.year.range[4]}. \Sexpr{publication.year.2018} studies have been published in 2018, none in 2019.\\
The top treatment effect measure (risk ratio, mean difference, hazard ratio etc.) abundances are summarized in Table \ref{outcome.measure.frequencies}. One can conclude of the table that roughly 31 \% of outcomes in the dataset are continuous and the rest being some sort of discrete or binary outcomes, most often binary (more than 65\%).

<<echo=FALSE, results='asis', warning =FALSE, message = FALSE>>=
print(xtable(outcome.measure.frequencies, label = "outcome.measure.frequencies", 
             caption = "Frequencies of outcome measures among results. n denotes the total number 
             of results with the outcome measure and percentage the percentage of the outcome measure,", 
             align = "llrr", digits = 1), include.rownames = F, size = "footnotesize")
@

The sample sizes among results vary to some extent. There are 5\% of treatment group sample sizes that are smaller than \Sexpr{treatment.group.size.range[1]}, 95\% smaller than \Sexpr{treatment.group.size.range[6]}. The first quartile is \Sexpr{treatment.group.size.range[2]}, the median \Sexpr{treatment.group.size.range[3]}, the mean \Sexpr{treatment.group.size.range[5]} and the third quartile \Sexpr{treatment.group.size.range[4]}. The large difference between median and mean is caused by very large groups with over 2,000,000 participants. Analogously, the quantiles of the total sample size are: 5\% quantile = \Sexpr{samplesize.range[1]}, first quartile = \Sexpr{samplesize.range[2]}, median = \Sexpr{samplesize.range[3]}, third quartile = \Sexpr{samplesize.range[4]} and 95\% = \Sexpr{samplesize.range[6]}. The mean is \Sexpr{samplesize.range[5]}. \\
There are \Sexpr{comp.range[1]} reviews with five or fewer results. The 5\% and 95\% quantiles are \Sexpr{comp.range[7]} and \Sexpr{comp.range[6]}. The mean and median number of results per review are \Sexpr{study.range[5]} and \Sexpr{study.range[3]}, and the quartiles are \Sexpr{comp.range[2]} and \Sexpr{comp.range[4]}. Similarly, the number of reviews with a maximum of two studies included is \Sexpr{study.range[1]}, the mean study number is \Sexpr{study.range[5]}, the median \Sexpr{study.range[3]} and the interquartile range \Sexpr{study.range[2]} and \Sexpr{study.range[4]} and the 95\% quantile \Sexpr{study.range[6]}. The discrepancy between mean and median is due to large reviews with a high number of studies and results, most extreme in %\citealp{largest.review} 
which is a systematic review about antibiotic prophylaxis for preventing infection after cesarean section, with 95 studies and 1,497 results in total.\\
For results to be suitable for usage in meta-analysis, they have to be identical with respect to comparison and outcome. The studies in the dataset that have the same comparison, outcome and subgroup can be pooled in a meta-analysis. This distinction is also used by Cochrane, \ie the meta-analyses are identical to the meta-analyses done in the systematic reviews.\\ %Another approach that is not made here is to analyze all subgroups together, which is possible if enough studies are given.
The size of a meta-analysis denotes how many results are included in a group. Table \ref{repr.groups} shows the number of meta-analysis with size $\geq n$ results.

@@

Initially, the analysis is restricted to results with \texttt{outcome.flag} \texttt{DICH}, \texttt{CONT} and \texttt{IV}. If \texttt{IV}, the only meta-analyses with \texttt{outcome.measure.merged} = \texttt{OR} / \texttt{RR} / \texttt{SMD} / \texttt{MD} / \texttt{Hazard Ratio} / \texttt{Rate Ratio} are used. 
\citealp{Ioannidis2007} outlined criteria for application of small study effect tests:
\begin{itemize}
\item \textbf{Sample size}: A meta-analysis is comprised of at least ten studies ($n$ = \Sexpr{m.a.largerten.count} remaining). 
\item \textbf{Study size}: The ratio between largest variance of an estimate and smallest variance of an estimate is larger than four ($n$ = \Sexpr{m.a.variance4.count} remaining).
\item \textbf{Significance}: At least one treatment effect has a $p$-value below the significance threshold 0.05 ($n$ = \Sexpr{m.a.one.sig.count} remaining)
\item \textbf{Heterogeneity}: The $I^2$ statistic of a given meta-analysis is smaller than 0.5, thus, the proportion of between study variance of the overall variance is smaller than 0.5 ($n$ = \Sexpr{m.a.smaller.5.count} remaining).
\end{itemize}
Additionally, the following criteria have been applied:
\begin{itemize}
\item \textbf{Sensitivity Analyses}: When the same results are used multiple times for different meta-analyses, only one is retained. More precisely, if a study hat the same \texttt{study.name} and same \texttt{effect}, it was considered a duplicate, and the smaller meta-analysis of the two was excluded. The intention is to exclude sensitivity analyses which are operated on subsets of the available results.
\item \textbf{Zero events}: In the case of binary outcomes, meta-analyses with zero events in any study and any group are excluded ($n$ = \Sexpr{both.arms.zero.events.count} out of meta-analyses with at least ten studies).
\item \textbf{No withdrawn reviews}: Reviews that have been withdrawn are not included.
\item \textbf{No adverse effects}: No results of adverse effects of treatment are used for meta-analyses. Exclusion is incomplete because only results with ``adverse'' in the comparison or outcome name could be removed, but not all adverse effect results are classified as such.
\end{itemize}

@@

    % Draw edges
    \path [line] (1) -- node [btw, xshift = -1.95cm] {no withdrawn reviews} (12);
    \path [line] (12) -- node [btw, xshift = -2.1cm] {only efficacy outcomes} (13);
    \path [line] (13) -- node [btw, xshift = -2cm] {\texttt{outcome.flag} restriction} (2);
    \path [line] (2) -- node [btw, xshift = -1.7cm] {study number $\geq$ 10}(3);
    \path [line] (3) -- node [btw, xshift = -1.6cm] {variance ratio $>$ 4} (4);
    \path [line] (4) -- node [btw, xshift = -2cm] {at least one significant result} (5);
    \path [line] (5) -- node [btw, xshift = -1.2cm] {no duplicates} (6);
    \path [line] (6) -- node [btw, xshift = -0.8cm] {$I^2$ $\leq$ 0.5} (7);

@@

\subsubsection{The Analysis Dataset}
The dataset that was ultimately tested and adjusted for publication bias comprises \Sexpr{dim(meta.f)[1]} meta-analyses and \Sexpr{format(dim(meta.data)[1], big.mark = ",")} results. The mean number of participants in the treatment group is \Sexpr{round(mean(meta.data$total1, na.rm = T),1)} vs \Sexpr{round(mean(data.ext2$total1, na.rm = T),1)} in the unrestricted dataset and the mean total number of participants \Sexpr{round(mean(meta.data$total1 + meta.data$total2),1)} vs \Sexpr{round(mean(data.ext2$total1 + data.ext2$total2),1)}. The mean publication year is \Sexpr{round(mean(meta.data$study.year, na.rm = TRUE))} vs \Sexpr{round(mean(data.ext2$study.year, na.rm = TRUE))} in the unrestricted dataset. \\
From the meta-analyses with incomplete data (\texttt{outcome.flag} == \texttt{IV}), there are \Sexpr{first.iv.outcome.count} with \\ \texttt{outcome.measure.merged} = \texttt{RR}, \Sexpr{second.iv.outcome.count} \texttt{SMD},  \Sexpr{third.iv.outcome.count} \texttt{Hazard Ratio}, \Sexpr{fourth.iv.outcome.count} \texttt{OR}, \Sexpr{fifth.iv.outcome.count} \texttt{MD} and \Sexpr{sixth.iv.outcome.count} \texttt{Rate Ratio}.

@@

Meta-analysis groups within a review were obtained by grouping by comparison, outcome and subgroup. The last step is optional, and the Cochrane Groups do also meta-analysis without taking into account subgroups. Subgroups are often specifications of treatment, \eg the form of the medication or the protocol. Thus, using the subgroups should increase the within-study homogeneity. However, the Cochrane disencourages meta-analyses based on subgroups only, because subgroups are often set up after the collection of the data analysis. Since the main interest of this study is not to precisely assess the efficacy of treatments, but the interest is merely on systematic differences between single studies investigating the same scientific question and not in the effect per se, it has been decided that the increase in precision is worthwhile the loss of a number of studies. While it is possible that the use of subgroups introduces bias in the meta-analysis, it is also possible that ignoring subgroups will do (which is one of the reasons why subgroups are analyses as well). When one subgroup has substantially different real treatment effects, and the specific properties influence study size, publication bias assessment fails. Subgroups are not indicated in \Sexpr{no.subgroup}\% of the meta-analyses in the analysis dataset 1, thus, there the analyses are identical to the overall analyses that the Cochrane Review Groups did. \\

@@

Details to Copas selection model algorithm and its application can be found in \citealp{limitmeta}. In short, two values for $a$ and $b$ in section \ref{sec:copas} were used; a limited range with $a$ between -1.7 and 2, and $b$ between 0.16 and 0.32 was applied first (analog to a most extreme selection process of $P$(select|small trial with sd = 0.4) = 0.1 and P(select|large trial w. sd  = 0.05) = 0.9). If the most extreme selection process is unable to pass the significance test of no small study effect ($p$-value > 0.1), then a wider range was applied ($a$  between -5.4 and 2 and $b$ between 0 and 0.32). If there is still no non-significant small study effect, the result was \texttt{NA}.

\section{Software}
All computations were performed in the \texttt{R} computing environment \citep{R.base}. The \texttt{R} packages \texttt{meta} \citep{meta.package} and \texttt{metafor} \citep{metafor.package} were used for meta-analysis, small study effect tests and adjustments. The excess significance test was adapted from \citealp{vanAert.2019}. For data manipulation procedures, the \texttt{tidyverse} packages were used \citep{tidyverse.package}, and for plotting the \texttt{ggplot2} package \citep{ggplot2}.\\

>>>>

missing.year.count <- sum(is.na(data$study.year)) #+ length(c(which(data$study.year < 1920), which(data$study.year > 2019)))

@@

\section{Cochrane Systematic Reviews}
Cochrane has specialized on systematic reviews in clinical science. Certain knowledge of standards and principles of the organization may help to understand the dataset. The following information stems from the Cochrane Handbook for Systematic Reviews \citep{cochrane.handbook}. \\
The definition of a systematic review is that it ``attempts to collate all empirical evidence that fits pre-specified eligibility criteria in order to answer a specific research question.'' Thus, the ``key properties of a review are'':

@@

\item MEDLINE includes over 16 million references to journal articles. 5,200 journals publishing in 27 languages are indexed for MEDLINE. PubMed gives access to a free version of MEDLINE with up-to-date citations. NLM gateway such as the Health Services Research Project, Meeting Abstracts and TOXLINE Subset for toxicology citations allows for search in both databases together with additional data from the US National Library of Medicine.
\item EMBASE. 4,800 journals publishing in 30 languages are indexed in EMBASE, which includes more than 11 million records from 1974 onward. EMBASE.com also includes 7 million unique records from MEDLINE (1966 up to date) together with its own records. Additionally, EMBASE Classic allows access to digitized records from 1947 to 1973. EMBASE and MEDLINE each have around 1,800 journals not indexed in any other database.

@@

\item Citation Indexes. The database lists articles published in around 6,000 journals with articles in which they have been cited and is available online as SciSearch. This form of search is known as cited reference searching.

@@

\item Grey Literature Databases. Approximately 10\% of the results in the Cochrane Library stems from conference abstracts and other grey literature. The Institute for Scientific and Technical Information in France provides access to entries of the previously closed System for Information on Grey Literature database of the European Association for Grey Literature Exploitation. Another source is the Healthcare Management Information Consortium (HMIC) database containing records from the Library and Information Services department of the Department of Health (DH) in England and the King's Fund Information and Library Service. The National Technical Information Service (NTIS) gives access to the results of US and non-US government-sponsored research, as well as technical report for most published results. References from newsletters, magazines and technical and annual reports in behavioral science, psychology and health are provided in the PsycEXTRA database which is linked to PsycINFO database.

@@

\section{Structure and Variables}
The dataset consists of \Sexpr{format(length(unique(data$id)), big.mark = ",")} systematic reviews from the Cochrane Library with \Sexpr{format(length(unique(data$study.name)), big.mark = ",")} studies and \Sexpr{format(dim(data)[1], big.mark = ",")} results. A result of a study can be a primary or secondary or safety outcome, thus studies can contribute multiple results. The studies too a very large extent randomized and investigate the effects of healthcare and medical interventions and treatments. The reference to the treatment may be a placebo control or a different intervention or treatment. A result can not only be about efficacy of the treatments, but also about safety (adverse effects).\\
It will be continued with an example form the dataset. In Table \ref{barbiturate.row}, two results from a systematic review about barbiturates are shown as they are given in the dataset. As can be seen, further specifications are provided by the variables in the columns. \\
The \texttt{comparison.name} variable specifies \textit{what kind} of treatments or interventions are compared, the \texttt{outcome.name} variable \textit{how} it is compared, and the \texttt{subgroup.name} variable (not indicated in table) if and to \textit{what experimental subgroup} the result belongs to. \\
The result is of a binary type, and the counts of events in the treatment group are in \texttt{events1} and of the control group in \texttt{events2} and the total number of participants are given in columns \texttt{total1} and \texttt{total2}. As can be seen, events denote here "death at the end of follow-up".

<<echo=FALSE, results = 'asis', warning =FALSE, message = FALSE>>=
print(xtable(barbi1, label = "barbiturate.row", digits = 0,
             caption = "Example of results from two primary studies that belong to the same comparison and outcome. Events denotes the count of events in the treatment group while Events c the count of events in the group compared to. Further descriptive variables have been ommitted"), 
      include.rownames = F, size = "scriptsize")
@

Results are part of studies that are again part of a (systematic) review. The general structure of a review is shown in Figure \ref{review.structure}.

\begin{figure}
\tikzstyle{every node}=[draw=black,thick,anchor=west]
\tikzstyle{selected}=[draw=red,fill=red!30]
\tikzstyle{optional}=[dashed,fill=gray!50]
\begin{tikzpicture}
[grow = right, anchor = west, 
  growth parent anchor=east, % added code
  parent anchor=east]
  \node {Review} [edge from parent fork right]
    child { node {Comparison 2}
      child { node {Outcome 2}}
      child { node {Outcome 1}
        child { node {Subgroup 2}}
        child { node {Subgroup 1}
          child  { node {Result 2}}
          child  { node {Result 1}}
          }}
    }
    child [missing] {}		
    child { node {Comparison 1  }};
\end{tikzpicture}
\caption{General structure of the database. Results from primary studies belong to the same comparison, outcome and subgroups, and can be used to estimate a combined effect in a meta-analysis.}
\label{review.structure}
\end{figure}

@@

\begin{table}[ht]
  \begin{center}
    \begin{tabular}{l l}
      \textbf{Variable} & \textbf{Description}\\
      \hline
      \texttt{id} & An id of the review for identification purposes.\\
      \hline
      \texttt{study.name} & Name of the study to which the result belongs.\\
      \texttt{study.year} & Year in which the study was published.\\
      \hline
      \texttt{comparison.name/.nr} & Specification of the interventions compared in the study and a \\ &unique number for the comparison.\\
      \texttt{comparison.id} & Specification of the comparison by a string of the type ``CMP-xxx'' \\ &for the xxx. comparison within the review.\\
      \texttt{outcome.name/.nr} & Specification by which outcome the interventions are compared\\ &and a unique number for the outcome.\\
      \texttt{outcome.id} & Specification of the outcome by a string of the type \\ &``CMP-xxx.xx'' for the xx. outcome of the xxx. comparison \\ &within the review.\\
      \texttt{subgroup.name/.nr} & Potentially indication of affiliation to subgroups and a unique \\ &number for the subgroup.\\
      \texttt{subgroup.id} & Specification of the comparison by a string of the type \\ &``CMP-xxx.yy.xx'' for the xx. subgroup for the yy. outcome \\ & of the xxx. comparison within the review.\\
      \texttt{outcome.measure} & Outcome measure, \eg risk ratio.\\
      \texttt{outcome.measure.merged} & Outcome measure, \eg risk ratio, merged such that each method is uniquely classified.\\
      \texttt{outcome.flag} & A outcome flag to simplify programming; \\ &\texttt{DICH} for binary outcomes with fully available information \\ &on event counts,
      as given in a two-by-two \\ &table. \\ &\texttt{CONT} for continuous outcomes with available means and \\ &standard deviations. \\ & \texttt{IV} for all results with effects and standard errors but without \\ & the data necessary for their computation. \\ &\texttt{IPD} for individual patient data.\\
      \texttt{effect} & Magnitude of the effect given in the quantity denoted by \\ &\texttt{outcome measure}.\\
      \texttt{se} & Standard error of the measure of the effect.\\
      \texttt{events1/events2} & The counts of patients with an outcome if measurement/outcome \\ &is binary or dichotomous (1 for treatment group and 2 for control group).\\
      \texttt{total1/total2} & Number of patients in groups.\\
      \texttt{mean1/mean2} & Mean of patient measurements if outcome is continuous.\\
      \texttt{sd1/sd2} & Standard deviation if outcome is continuous.
    \end{tabular}
  \caption{Dataset variable names and descriptions  \label{variable}}
  \label{variable}
  \end{center}
\end{table}

@@

The primary studies that are included in the reviews and have been published are most often from the years after 1980 (5\% quantile = \Sexpr{publication.year.range[1]}, 95\% quantile = \Sexpr{publication.year.range[6]},). The median of the publication years is \Sexpr{publication.year.range[3]}, the mean \Sexpr{round(publication.year.range[5])} and the quartiles are \Sexpr{publication.year.range[2]} and \Sexpr{publication.year.range[4]}. \Sexpr{format(publication.year.2018$n, big.mark = ",")} studies have been published in 2018.\\
The most frequent outcome measures are summarized in Table \ref{outcome.measure.frequencies}. One can conclude of the table that roughly 31 \% of outcomes in the dataset are continuous and the rest being some sort of discrete or binary outcomes, most often binary (more than 65\%).

<<echo=FALSE, results='asis', warning =FALSE, message = FALSE>>=
print(xtable(outcome.measure.frequencies, label = "outcome.measure.frequencies", 
             caption = "Frequencies of outcome measures among results.", 
             align = "llrr", digits = 1), include.rownames = F, size = "footnotesize")
@

The sample sizes among results vary to some extent. There are 5\% of treatment group sample sizes that are smaller than \Sexpr{treatment.group.size.range[1]}, 95\% smaller than \Sexpr{treatment.group.size.range[6]}. The first quartile is \Sexpr{treatment.group.size.range[2]}, the median \Sexpr{treatment.group.size.range[3]}, the mean \Sexpr{round(treatment.group.size.range[5])} and the third quartile \Sexpr{treatment.group.size.range[4]}. The large difference between median and mean is caused by very large groups with over 2,000,000 participants. Analogously, the quantiles of the total sample size are: 5\% quantile = \Sexpr{samplesize.range[1]}, first quartile = \Sexpr{samplesize.range[2]}, median = \Sexpr{samplesize.range[3]}, third quartile = \Sexpr{samplesize.range[4]} and 95\% = \Sexpr{samplesize.range[6]}. The mean is \Sexpr{round(samplesize.range[5])}. \\
There are \Sexpr{comp.range[1]} reviews with five or fewer results. The 5\% and 95\% quantiles are \Sexpr{comp.range[7]} and \Sexpr{comp.range[6]}. The mean and median number of results per review are \Sexpr{study.range[5]} and \Sexpr{study.range[3]}, and the quartiles are \Sexpr{comp.range[2]} and \Sexpr{comp.range[4]}. Similarly, the number of reviews with a maximum of two studies included is \Sexpr{format(study.range[1], big.mark = ",")}, the mean study number is \Sexpr{study.range[5]}, the median \Sexpr{study.range[3]} and the interquartile range \Sexpr{study.range[2]} and \Sexpr{study.range[4]} and the 95\% quantile \Sexpr{study.range[6]}. The discrepancy between mean and median is due to large reviews with a high number of studies and results, most extreme in %\citealp{largest.review} 
which is a systematic review about antibiotic prophylaxis for preventing infection after cesarean section, with 95 studies and 1,497 results in total.\\
For results to be suitable for usage in meta-analysis, they have to be identical with respect to comparison and outcome. The studies in the dataset that have the same comparison, outcome and subgroup can be pooled in a meta-analysis. This distinction is also used by Cochrane, \ie the meta-analyses are identical to the meta-analyses done in the systematic reviews.\\ %Another approach that is not made here is to analyze all subgroups together, which is possible if enough studies are given.
The size of a meta-analysis denotes how many results are included in a group. Table \ref{repr.groups} shows the number of meta-analysis with size $\geq n$ results.

@@

The analysis includes all results with \texttt{outcome.flag} \texttt{DICH}, \texttt{CONT} and \texttt{IV}. If outcome is \texttt{IV}, the only meta-analyses with \texttt{outcome.measure.merged} = \texttt{OR} / \texttt{RR} / \texttt{SMD} / \texttt{MD} / \texttt{Hazard Ratio} / \texttt{Rate Ratio} are used. 
\citealp{Ioannidis2007} outlined criteria for application of small study effect tests:
\begin{itemize}
\item \textbf{Sample size}: A meta-analysis is comprised of at least ten studies ($n$ = \Sexpr{format(m.a.largerten.count, big.mark = ",")} remaining). 
\item \textbf{Study size}: The ratio between largest variance of an estimate and smallest variance of an estimate is larger than four ($n$ = \Sexpr{format(m.a.variance4.count, big.mark = ",")} remaining).
\item \textbf{Significance}: At least one treatment effect has a $p$-value below the significance threshold 0.05 ($n$ = \Sexpr{format(m.a.one.sig.count, big.mark = ",")} remaining)
\item \textbf{Heterogeneity}: The $I^2$ statistic of a given meta-analysis is smaller than 0.5, thus, the proportion of between study variance of the overall variance is smaller than 0.5 ($n$ = \Sexpr{format(m.a.smaller.5.count, big.mark = ",")} remaining).
\end{itemize}
Additionally, the following criteria have been applied:
\begin{itemize}
\item \textbf{Sensitivity Analyses}: When the same results are used multiple times for different meta-analyses, only one is retained. More precisely, if a study hat the same \texttt{study.name} and same \texttt{effect}, it was considered a duplicate, and the smaller meta-analysis of the two was excluded. The intention is to exclude sensitivity analyses which are operated on subsets of the available results.
\item \textbf{Zero events}: In the case of binary outcomes, meta-analyses with zero events in any study and any group are excluded ($n$ = \Sexpr{both.arms.zero.events.count} out of meta-analyses with at least ten studies).
\item \textbf{No withdrawn reviews}: Reviews that have been withdrawn are not included.
\item \textbf{No adverse effects}: No results of adverse effects of treatment are used for meta-analyses.we could thus clearly identify many safety results but this may be incomplete when safety outcomes are insufficiently declared, for example ``headache''.
\end{itemize}

@@

    % Draw edges
    \path [line] (1) -- node [btw, xshift = -2.3cm] {exclusion of withdrawn reviews} (12);
    \path [line] (12) -- node [btw, xshift = -2.1cm] {only efficacy outcomes} (13);
    \path [line] (13) -- node [btw, xshift = -2cm] {\texttt{outcome.flag} restriction} (2);
    \path [line] (2) -- node [btw, xshift = -1.7cm] {study number $\geq$ 10}(3);
    \path [line] (3) -- node [btw, xshift = -1.6cm] {variance ratio $>$ 4} (4);
    \path [line] (4) -- node [btw, xshift = -2cm] {at least one significant result} (5);
    \path [line] (5) -- node [btw, xshift = -1.2cm] {no duplicates} (6);
    \path [line] (6) -- node [btw, xshift = -0.8cm] {$I^2$ $\leq$ 0.5} (7);

@@

\subsubsection{The Analysis Dataset}
The dataset that was ultimately tested and adjusted for publication bias comprises \Sexpr{format(dim(meta.f)[1], big.mark = ",")} meta-analyses and \Sexpr{format(dim(meta.data)[1], big.mark = ",")} results. The mean number of participants in the treatment group is \Sexpr{round(mean(meta.data$total1, na.rm = T),1)} vs \Sexpr{round(mean(data.ext2$total1, na.rm = T),1)} in the complete dataset and the mean total number of participants \Sexpr{round(mean(meta.data$total1 + meta.data$total2),1)} vs \Sexpr{round(mean(data.ext2$total1 + data.ext2$total2),1)}. The mean publication year is \Sexpr{round(mean(meta.data$study.year, na.rm = TRUE))} vs \Sexpr{round(mean(data.ext2$study.year, na.rm = TRUE))} in the complete dataset. \\
From the meta-analyses with incomplete data (\texttt{outcome.flag} == \texttt{IV}), there are \Sexpr{first.iv.outcome.count} with \\ \texttt{outcome.measure.merged} = \texttt{RR}, \Sexpr{second.iv.outcome.count} \texttt{SMD},  \Sexpr{third.iv.outcome.count} \texttt{Hazard Ratio}, \Sexpr{fourth.iv.outcome.count} \texttt{OR}, \Sexpr{fifth.iv.outcome.count} \texttt{MD} and \Sexpr{sixth.iv.outcome.count} \texttt{Rate Ratio}.

@@

Meta-analysis within a review were obtained by grouping by comparison, outcome and subgroup. The last step is optional, and the Cochrane Groups do also meta-analysis without taking into account subgroups. Subgroups are often specifications of treatment, \eg the form of the medication or the protocol. Thus, using the subgroups should increase the within-study homogeneity. However, the Cochrane disencourages meta-analyses based on subgroups only, because subgroups are often set up after the collection of the data analysis. Since the main interest of this study is not to precisely assess the efficacy of treatments, but the interest is merely on systematic differences between single studies investigating the same scientific question and not in the effect per se, it has been decided that the increase in precision is worthwhile the loss of a number of studies. While it is possible that the use of subgroups introduces bias in the meta-analysis, it is also possible that ignoring subgroups will do (which is one of the reasons why subgroups are analyses as well). When one subgroup has substantially different real treatment effects, and the specific properties influence study size, publication bias assessment fails. Subgroups are not indicated in \Sexpr{no.subgroup}\% of the meta-analyses in the analysis dataset 1, thus, there the analyses are identical to the overall analyses that the Cochrane Review Groups did. \\

@@

Details to Copas selection model algorithm and its application can be found in \citet{limitmeta}. In short, two values for $a$ and $b$ in section \ref{sec:copas} were used; a limited range with $a$ between -1.7 and 2, and $b$ between 0.16 and 0.32 was applied first (analog to a most extreme selection process of $P$(select|small trial with sd = 0.4) = 0.1 and P(select|large trial w. sd  = 0.05) = 0.9). If the most extreme selection process is unable to pass the significance test of no small study effect ($p$-value > 0.1), then a wider range was applied ($a$  between -5.4 and 2 and $b$ between 0 and 0.32). If there is still no non-significant small study effect, the result was \texttt{NA}.

\section{Software}
All computations were performed in the \texttt{R} computing environment \citep{R.base}. The \texttt{R} packages \texttt{meta} \citep{meta.package} and \texttt{metafor} \citep{metafor.package} were used for meta-analysis, small study effect tests and adjustments. The excess significance test was adapted from \citet{vanAert.2019}. For data manipulation procedures, the \texttt{tidyverse} packages were used \citep{tidyverse.package}, and for plotting the \texttt{ggplot2} package \citep{ggplot2}.\\
